An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-10 EconGrowth.Rnw
Now including graph of rho (sigma) vs. delta for CES without energy. Not a very exciting graph, but drawing it all the same.

Coefficients for each resampled CES model (without energy)
are shown in Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph} 
and \ref{fig:CES_sigma_1_delta_1_Cloud_Graph}.

@@

>>>>

Coefficients for each resampled CES model (without energy)
are shown in 
Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph}--\ref{fig:CES_sigma_delta_Cloud_Graph}.

@@

The next graph is not particularly interesting, 
because $\delta \rightarrow 1.0$, 
$\rho \rightarrow -1$, and 
$\sigma \rightarrow \infty$
for the CES without energy model.

<<CES_sigma_delta_Cloud_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="CES (without energy) resample model parameters $\\rho$ and $\\delta$.">>=
cesSigmaDeltaResamplePlot(energyType=NA)
@
